---
title: "Lab9"
author: "Thomas Wilson"
date: "11/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringr)
library(tidyverse)
x <- c("apple", "banana", "pear")
str_view(x, "an")
## ---The next step up in complexity is ., which matches any character (except a newline)---
str_view(x, ".a.")
dot <- "\\."
writeLines(dot)
```
```{r}
x <- c("abc", "a.c", "bef")
## ---create the regular expression \. we need the string "\\.".---
str_view(x, "a\\.c")
x <- "a\\b"
writeLines(x)
str_view(x, "\\\\")
```
## ---14.3.1.1 Exercises---

## ---1. Explain why each of these strings don’t match a \: "\", "\\", "\\\".---
  These don't match a :\" because the a "\" is used as an escape character, and therefor each reg expression needs a "\", which results in the need for 4 backslashes
  
## ---2. How would you match the sequence "'\?----
  str_view("\"'\\", "\"'\\\\", match = TRUE)

## ---3. What patterns will the regular expression \..\..\.. match? How would you represent it as a string?---
  It will match any patterns that are a dot followed by any character, repeated three times.

str_view(c(".a.b.c", ".a.b", "....."), c("\\..\\..\\.."), match = TRUE)
```{r}
x <- c("apple", "banana", "pear")
## ---if you begin with power (^), you end up with money ($).---
str_view(x, "^a")
str_view(x, "a$")
x <- c("apple pie", "apple", "apple cake")
str_view(x, "apple")
str_view(x, "^apple$")
```
14.3.2.1 Exercises

1.How would you match the literal string "$^$"?
  str_view(c("$^$", "ab$^$sfas"), "^\\$\\^\\$$", match = TRUE)

2.Given the corpus of common words in stringr::words, create regular expressions that find all words that:
Start with “y”.
  str_view(stringr::words, "^y", match = TRUE)
End with “x”
  str_view(stringr::words, "x$", match = TRUE)
Are exactly three letters long are
  str_view(stringr::words, "^...$", match = TRUE)
Are exactly three letters long. (Don’t cheat by using str_length()!)
Have seven letters or more.
  str_view(stringr::words, ".......", match = TRUE)
```{r}
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
str_view(x, ".[*]c")
str_view(x, "a[ ]")
x <- c("grey", "gray")
str_view(x, "gr(e|a)y")

## ---\d : matches any digit. \s : matches any whitespace (e.g. space, tab, newline). [abc] : matches a, b, or c.[^abc] : matches anything except a, b, or c. --- 
```
  14.3.3.1 Exercises

1. Create regular expressions to find all words that:
Start with a vowel.
  str_subset(stringr::words, "^[aeiou]")
That only contain consonants. (Hint: thinking about matching “not”-vowels.)
  str_subset(stringr::words, "[aeiou]", negate=TRUE)
End with ed, but not with eed.
  str_subset(stringr::words, "[^e]ed$")
End with ing or ise.
  str_subset(stringr::words, "i(ng|se)$")
2. Empirically verify the rule “i before e except after c”.
  length(str_subset(stringr::words, "(cie|[^c]ei)"))
3. Is “q” always followed by a “u”?
  In the stringr::words dataset, yes.
4. Write a regular expression that matches a word if it’s probably written in British English, not American English.
  str_subset(stringr::words, ou|ise$|ae|oe|yse$)
5. Create a regular expression that will match telephone numbers as commonly written in your country.
  str_view(x, "[0-9][0-9][0-9]-[0-9][0-9][0-9]-[0-9][0-9][0-9][0-9]")
```{r}

## --- [?: 0 or 1] [+: 1 or more] [*: 0 or more]

x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "CC?")
str_view(x, "CC+")
str_view(x, 'C[LX]+')
str_view(x, "C{2}")
str_view(x, "C{2,}")
str_view(x, "C{2,}")
str_view(x, 'C{2,3}?')
str_view(x, 'C[LX]+?')
```
14.3.4.1 Exercises

Describe the equivalents of ?, +, * in {m,n} form.
Describe in words what these regular expressions match: (read carefully to see if I’m using a regular expression or a string that defines a regular expression.)
^.*$
  will match any string
"\\{.+\\}"
  will match any string with curly braces surrounding at least one character
\d{4}-\d{2}-\d{2}
  will match four digits followed by a hyphen, followed by two digits followed by a hyphen, followed by another two digits. This is a regular expression that can match dates formatted like “YYYY-MM-DD” (“%Y-%m-%d”)
"\\\\{4}"
Create regular expressions to find all words that:
Start with three consonants.
  str_view(words, "^[^aeiou]{3}", match = TRUE)
Have three or more vowels in a row.
  str_view(words, "[aeiou]{3}", match = TRUE)
Have two or more vowel-consonant pairs in a row.
  str_view(words, "([aeiou][^aeiou]){2,}", match = TRUE)
Solve the beginner regexp crosswords at https://regexcrossword.com/challenges/beginner.
```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```
Describe, in words, what these expressions will match:
(.)\1\1
  The same character appearing three times in a row
"(.)(.)\\2\\1"
  A pair of characters followed by the same pair of characters in reversed order
(..)\1
  Any 2 characters repeated
"(.).\\1.\\1"
   character followed by any character, the original character, any other character, the original character again
"(.)(.)(.).*\\3\\2\\1"
  Three characters followed by zero or more characters of any kind followed by the reverse order
Construct regular expressions to match words that:
Start and end with the same character.
  str_subset(words, "^(.)((.*\\1$)|\\1?$)")
Contain a repeated pair of letters (e.g. “church” contains “ch” repeated twice.)
  str_subset(words, "([A-Za-z][A-Za-z]).*\\1")
Contain one letter repeated in at least three places (e.g. “eleven” contains three “e”s.)
  str_subset(words, "([a-z]).*\\1.*\\1")
```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
sum(str_detect(words, "^t"))
mean(str_detect(words, "[aeiou]$"))
no_vowels_1 <- !str_detect(words, "[aeiou]")
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
words[str_detect(words, "x$")]
str_subset(words, "x$")
df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))
x <- c("apple", "banana", "pear")
str_count(x, "a")
mean(str_count(words, "[aeiou]"))
df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
str_count("abababa", "aba")
str_view_all("abababa", "aba")
```
14.4.1.1 Exercises

For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.
Find all words that start or end with x.
  words[str_detect(words, "^x|x$")]
  start_with_x <- str_detect(words, "^x")
end_with_x <- str_detect(words, "x$")
  str_subset(words, "^[aeiou].*[^aeiou]$") %>% head()
words[start_with_x | end_with_x]
  start_with_vowel <- str_detect(words, "^[aeiou]")
end_with_consonant <- str_detect(words, "[^aeiou]$")
words[start_with_vowel & end_with_consonant] %> head()
Find all words that start with a vowel and end with a consonant.
  
Are there any words that contain at least one of each different vowel?
What word has the highest number of vowels? What word has the highest proportion of vowels? (Hint: what is the denominator?)
  vowels <- str_count(words, "[aeiou]")
words[which(vowels == max(vowels))]
prop_vowels <- str_count(words, "[aeiou]") / str_length(words)
words[which(prop_vowels == max(prop_vowels))]
```{r}
length(sentences)
head(sentences)
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
colour_match
has_colour <- str_subset(sentences, colour_match)
matches <- str_extract(has_colour, colour_match)
head(matches)
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
str_extract(more, colour_match)
str_extract_all(more, colour_match)
str_extract_all(more, colour_match, simplify = TRUE)
x <- c("a", "a b", "a b c")
str_extract_all(x, "[a-z]", simplify = TRUE)
```
14.4.2.1 Exercises

In the previous example, you might have noticed that the regular expression matched “flickered”, which is not a colour. Modify the regex to fix the problem.
  colour_match2 <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")
colour_match2
  more2 <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more2, colour_match2, match = TRUE)
From the Harvard sentences data, extract:
The first word from each sentence.
  str_extract(sentences, "[A-ZAa-z]+")
All words ending in ing.
  pattern <- "\\b[A-Za-z]+ing\\b"
sentences_with_ing <- str_detect(sentences, pattern)
unique(unlist(str_extract_all(sentences[sentences_with_ing], pattern))) 
All plurals.
  unique(unlist(str_extract_all(sentences, "\\b[A-Za-z]{3,}s\\b")))
```{r}
noun <- "(a|the) ([^ ]+)"

has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
has_noun %>% 
  str_match(noun)
tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```
14.4.3.1 Exercises

Find all words that come after a “number” like “one”, “two”, “three” etc. Pull out both the number and the word.
  numword <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, numword)] %>%
  str_extract(numword)
Find all contractions. Separate out the pieces before and after the apostrophe.
  contraction <- "([A-Za-z]+)'([A-Za-z]+)"
sentences[str_detect(sentences, contraction)] %>%
  str_extract(contraction) %>%
  str_split("'")
```{r}
x <- c("apple", "pear", "banana")
str_replace(x, "[aeiou]", "-")
str_replace_all(x, "[aeiou]", "-")
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))
sentences %>% 
  str_replace("([^ ]+) ([^ ]+) ([^ ]+)", "\\1 \\3 \\2") %>% 
  head(5)
```
  14.4.4.1 Exercises

Replace all forward slashes in a string with backslashes.
  str_replace_all("past/present/future", "/", "\\\\")
Implement a simple version of str_to_lower() using replace_all().
  replacements <- c("A" = "a", "B" = "b", "C" = "c", "D" = "d", "E" = "e",
                  "F" = "f", "G" = "g", "H" = "h", "I" = "i", "J" = "j", 
                  "K" = "k", "L" = "l", "M" = "m", "N" = "n", "O" = "o", 
                  "P" = "p", "Q" = "q", "R" = "r", "S" = "s", "T" = "t", 
                  "U" = "u", "V" = "v", "W" = "w", "X" = "x", "Y" = "y", 
                  "Z" = "z")
lower_words <- str_replace_all(words, pattern = replacements)
head(lower_words)
Switch the first and last letters in words. Which of those strings are still words?
  Swapped <- str_replace_all(words, "^([A-Za-z])(.*)([A-Za-z])$", "\\3\\2\\1")
  intersect(swapped, words)
```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
fields <- c("Name: Hadley", "Country: NZ", "Age: 35")
fields %>% str_split(": ", n = 2, simplify = TRUE)
x <- "This is a sentence.  This is another sentence."
str_view_all(x, boundary("word"))
str_split(x, " ")[[1]]
str_split(x, boundary("word"))[[1]]
```
14.4.5.1 Exercises

Split up a string like “apples, pears, and bananas” into individual components.
Why is it better to split up by boundary(“word”) than " "?
  x <- c("apples, pears, and bananas")
str_split(x, ", +(and +)?")[[1]]
What does splitting with an empty string ("") do? Experiment, and then read the documentation.
  It records only words, and takes into consideration of punctuation and grammar
```{r}

```
  


